Universal regime transition for water resources utilization in developing river basins

### 2020-09-29 tex/main/manuscript.tex
add a paragraph in discussion to give a interpret

%tag 结果2
\subsection*{Differences between water utilization regimes}
% 在不同的维度下各阶段进行对比，可以发现不同的水资源利用体系间存在明显差异。
The differences between the water utilization regimes are reflected in changes of all three dimensions.
\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/dimensions.pdf}
	\caption{
		Changes in different dimensions of water resources utilization regimes and their main contributors.
		\textbf{A,} changes of water utilization stress, indicated by unstandardized scarcity-flexibility-variability water stresses index (SFV-index, see \textit{Methods} and \textit{SI Appendix} Method S4).
		\textbf{B,} changes of water utilization priority, indicated by non-provisioning water shares (see Methods S4).
		\textbf{C,} changes of water utilization configuration, indicated by unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
		\textbf{D,} Main impact factors to water utilization stresses in each period or region, and their change contributions to unstandardized SFV-index.
		\textbf{E,} Main impact water uses to water utilization tendentiousnesses, and their change contributions to non-provisioning water shares.
		\textbf{F,} Main impact factors to water utilization patterns, and their change contributions of related unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
		}
	\label{fig:dimensions}
\end{figure*}
% 从阶段一到阶段二，水资源压力的变化最为明显
Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water utilization stress(Figure~\ref{fig:dimensions}A), which is determined by a combination of scarcity, flexibility and variability (Figure~\ref{fig:dimensions}D).   
% 1. 水资源丰富，耗水量少且灵活用水
In the P1, natural surface water resources were rather abundant with fewer water consumptions (\textit{SI Appendix} Fig. S3) and most of which were flexible water utilization (\textit{SI Appendix} Fig. S4). During the P1 and even P2, however, water consumption increases rapidly and natural surface water resources decreases at the same time, making water increasingly scarce. Opposite effect to that, numerous reservoirs built reduced the variability of water resources by boosting storage capacities, but there are much fewer reservoirs built in P2 (\textit{SI Appendix S5}). As a result, water utilization stress decreases during P1, but begins to rise rapidly in P2.

@@

@@

% 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。
Throughout the above transition phases towards dualistic water cycle, three dimensions of water utilization regime are various in discipline of evolution, corresponding to typical changes within the Yellow River Basins as an example (Figure~\ref{fig:dimensions}). 
% 水资源压力
(1) Firstly, although stresses on water resources increases by economic expansion boosting water demands, socio-economic progress responding to resource scarcity by better management and efficiency. Water resources were becoming more scarce in the Yellow River Basin from P1 to P3, but the expansion of farmland, the construction of reservoirs, and the increase in water use efficiency became responses to different water utilization stresses in aspects (Figure~\ref{fig:Causes}). Since the scarcity of water resources is directly perceptible and sensitive for utilization, its stresses on societies is one of the most striking drivers to regime shifts within human-water systems \cite{qinFlexibilityIntensityGlobal2019}.
% 水资源倾向性
(2) Secondly, the non-provisioning part of water demands growths with secondary and tertiary industries developing, leading priority of water utilization continually tilted to the socio-economic part. As original region of Ancient Chinese Civilization, the Yellow River Basin used to be dominated by agricultural but in its way to an energy industry zone now \cite{WillEnergyBases}. As a result, saving water consumption in agriculture and making concessions for industry and energy is widely recognized as solutions for the competing \cite{xiangWillEnergyIndustry2016,bebbWaterRightsTransfers2011}. Anyhow, this changes of priority reflect a truth that growing socio-economic parts are throwing feedbacks to scarcity of water resources and contributing to regime shifts.
% 水资源格局
(3) Thirdly, with closer socio-economic ties and stiffer competition between regions and sectors, the geographic scope of water resource supply and demand allocation is expanding, leading to changing patterns of water utilization. In the Yellow River Basin, the gap in water consumptions between regions and sectors are narrowing, as the result of a carefully designed allocation \cite{wangThirtyYearsYellow2018}. However, the allocation of water utilization is determined on the basis of regional and sectoral economic contexts and development trajectories\cite{wangThirtyYearsYellow2018}. The changes in water utilization patterns along with regime shifts, therefore, are the outcomes of feedback loops within complex human-water systems.

@@

	\subsection*{Integrated Water Resources Utilization (IWRU) Index}
	The Integrated Water Resources Utilization (IWRU) Index consists of three dimensions (stresses, tendentiousnesses and patterns, denoted by sub-indicators correspondingly). Assuming they have equal weights, we log-transformed and standardized the three sub-indicators for elimination of differences between indicators. It means for each indicator $I_{sub}$, we performed:
	$$ I' = log(I_{sub}) $$
	$$ I = (I' - I'_{min}) / (I'_{max}-I'_{min})$$
	where $I$ is standardized series for $I_{sub}$.
	Then, since we assumed different relationships between development and sub-indicators, we added them together in equal weights:
	$$ IWRU = \sum_{i}^3 I'_i $$
	where $i$ is stress, priority or configuration, and $I'_i$ is standardized sub-indicator of them. A brief description of the sub-indicators used to measure each dimension follows (see SI Methods. S3 for more details).

@@

	\subsubsection*{Sub-indicator of Patterns}
	To description of patterns between regions or sections, we designed an indicator by imitation of information entropy (Allocational Entropy Metric, see supplementary document: Methods S4). Assuming the most egalitarian water allocation is assumed to be that each region or sectoral development utilizes the same proportion of water resources (the case of maximum entropy). The ratio between the actual water allocation entropy and this maximum entropy is the allocation entropy index.
	$$ ratio = \frac{Entropy}{Entropy_{max}} $$
	where $Entropy$ and $Entropy_{max}$ are entropy and maximum entropy of water distributions, respectively. They can be calculated by:
	$$ Entropy = \sum_{i=1}^n \sum_{j=1}^m -log(p_{ij}) * p_{ij} $$
	$$ Entropy_{max} = n * \sum_{j=1}^m -\frac{p_j}{n} * log(\frac{p_j}{n}) $$ 
	where $p_j$ and $p_ij$ are proportions of water use in sector $j$ and region $i$:
	$$ p_j = \frac{\sum_{i=1}^n WU_j}{\sum_{i=1}^n WU} $$
	$$ p_{ij} = \frac{WU_{ij}} {\sum_{i=1}^n \sum_{j=1}^m WU_{ij}} $$
	where $n$ is the total number of regions ($n=4$ here, see supplementary Methods. S1) and $m$ is the total number of sectors ($m=4$ here, see supplementary Methods. S2).

>>>>

%tag 结果2
\subsection*{Differences between water utilization regimes}
% 在不同的维度下各阶段进行对比，可以发现不同的水资源利用体系间存在明显差异。
The differences between the water utilization regimes are reflected in changes of all three dimensions.
\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/dimensions.pdf}
	\caption{
		Changes in different dimensions of water resources utilization regimes and their main contributors.
		\textbf{A,} changes of water utilization stress, indicated by unstandardized scarcity-flexibility-variability water stresses index (SFV-index, see \textit{Methods} and \textit{SI Appendix} Method S4).
		\textbf{B,} changes of water utilization priority, indicated by non-provisioning water shares (see Methods S4).
		\textbf{C,} changes of water utilization configuration, indicated by unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
		\textbf{D,} Main impact factors to water utilization stresses in each period or region, and their change contributions to unstandardized SFV-index.
		\textbf{E,} Main impact water uses to water utilization priority, and their change contributions to non-provisioning water shares.
		\textbf{F,} Main impact factors to water utilization configurations, and their change contributions of related unstandardized distribution information entropy index (\textit{Methods} and \textit{SI Appendix} Method S4).
		}
	\label{fig:dimensions}
\end{figure*}
% 从阶段一到阶段二，水资源压力的变化最为明显
Moving from the regime in P1 to P2, the most striking change is the reversal of the trend in water utilization stress(Figure~\ref{fig:dimensions}A), which is determined by a combination of scarcity, flexibility and variability (Figure~\ref{fig:dimensions}D).   
% 1. 水资源丰富，耗水量少且灵活用水
In the P1, natural surface water resources were rather abundant with fewer water consumptions (\textit{SI Appendix} Fig. S3) and most of which were flexible water utilization (\textit{SI Appendix} Fig. S4). During the P1 and even P2, however, water consumption increases rapidly and natural surface water resources decreases at the same time, making water increasingly scarce. Opposite effect to that, numerous reservoirs built reduced the variability of water resources by boosting storage capacities, but there are much fewer reservoirs built in P2 (\textit{SI Appendix S5}). As a result, water utilization stress decreases during P1, but begins to rise rapidly in P2.

@@

\subsection*{Interpret of regime shifts within YRB}
% 我们发明的指数能将三个维度的变化捕捉到。
The IWRU index captures, with three dimensions (stress, priority and configuration), the complex human-water feedbacks that links social development and water resources utilization. 
% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态
Our results show that three distinct regimes of water utilization within YRB, which have been driven by different causes regarding the three above dimensions.
% 在第一个稳态时期（即P1: before 1978），黄河流域农业的GDP贡献曾达到，超过经济效率通常更高的工业和服务业。
Before 1978, the contribution of agriculture in the YRB to GDP was nearly a half (46\% in 1965), much higher than that of industry or services (33\% and 26\% in 1965, respectively see \textit{SI Appendix} fig. S8). 
% 考虑到彼时下游的工业用水尚未从黄河取水，且按省估计的夸张，这个数字仍远远低估了黄河流域的社会发展对农业的依赖。
Given that downstream industrial water had not depended on Yellow River yet, and the provincial estimates are exaggerated in industrial or services GDP (\textit{SI Appendix} Methods S3), this figure still greatly understates the dependence on agriculture for social development then.
% 因此那时候，黄河流域主要管理组织黄河水利委员会（）的主要工作之一是成立水利机构从事水利建设，而新建设的水库也多分布于高需水的区域。
At that time, one of the main tasks of the Yellow River Conservancy Commission (YRCC), therefore, was to set up agencies for water infrastructure (\textit{SI Appendix} Table S2), and the new reservoirs were mostly distributed in regions with high water demands (Figure~\ref{fig:Causes} C). 
% 结果是，该稳态的主要特征表现为灌溉用水的迅速扩张，以支持农业发展。
As a result, this regime is characterized by a rapid expansion of irrigation water to support agricultural development.

% 但因水资源危机的到来，上一制度与扩张性的农业发展随之结束，此时黄河耗水量已占天然径流量的约77%。
% 1972年，黄河首次断流19天，断流长度达310km，并连续多年断流。
The regime, however, nearly came to an end with the water resource crisis, as the water consumption of the Yellow River had accounted for about 80\% of the natural runoff. In 1972, the Yellow River was cut off for the first time with a length of 310 km for 19 days, and continued to be cut off for many years since then (\textit{SI Appendix} Fig. S9). 
% 来到1978年的制度时，黄委会领导改组，并接到水利部的批示，要求恢复和加强水文和流域管理相关的工作，
Came to the regime since 1978, the YRCC undergone a reorganization and received instructions from the Ministry of Water Resources (called Ministry of Water Resources and Electric Power then) to resume and strengthen work related to hydrology and basin management in YRB.
% 自此，稳态农业的扩张趋势得到了遏制（图causes），大部分流域尺度及以上的法律规章从此开始逐步推行，并在1987年提出了影响深远的“87分水方案”，为流域内各省份限定了可引水量
Since then, the expansion trend of agriculture has been contained in this regime (Figure~\ref{fig:Causes}A), while the importance of industry began to increase with the opening up of Chinese market. In addition, most laws and regulations have been gradually implemented (\textit{SI Appendix} Table 3 and Fig. S10). For an example, the far-reaching “87 Water Diversion Scheme”, which was put forward in 1987, limited the amount of water withdraw for each province as a constant in the YRB.

% 下一次稳态转换直到1993年左右才由用水效率的显著提升而带来。
The next regime shift was not occurred by a significant increase in water use efficiency in about 1993. 
% 此时在经历了十余年发展后，经济的重心已经倾向了工业和服务业，农业在GDP中的比重此时只占23%。
After more than a decade of development, the focus of economy had shifted to industry and services whose contribution of GDP in YRB are 45\% and 31\%, while agriculture accounting for only 23\% (\textit{SI Appendix} Fig.S8).
% 经济增长的同时，工业用水需求也迅速增加，两者推动了用水效率低下的农业实施节水改革。
A rapid increase in industrial demand for water has been accompanied by economic growth, which had led to water-saving reforms in inefficient agriculture. As a result, water use efficiency improved significantly in both agriculture and industry during the third regime (Figure~\ref{fig:Causes}A and Figure~\ref{fig:Causes}B), with engineered water-efficient irrigation reaching nearly half (48.6\%) of the total irrigated area (\textit{SI Appendix} Fig. S7), allowing the average water consumption per unit of irrigated area to drop about tenfold (Figure~\ref{fig:Causes}A).

In short, agricultural expansion, industrial services expansion, water resources management, as well as scientific and technological progress and water use efficiency improvement, have driven the YRB to change regimes twice between 1965 and 2013, which had been along with social development in different aspects and can be interpreted by a transition process.

@@

% 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。
Throughout the above transition phases towards dualistic water cycle, three dimensions of water utilization regime are various in discipline of evolution, corresponding to typical changes within the Yellow River Basins as an example (Figure~\ref{fig:dimensions}). 
% 水资源压力
(1) Firstly, although stresses on water resources increases by economic expansion boosting water demands, socio-economic progress responding to resource scarcity by better management and efficiency. Water resources were becoming more scarce in the Yellow River Basin from P1 to P3, but the expansion of farmland, the construction of reservoirs, and the increase in water use efficiency became responses to different water utilization stresses in aspects (Figure~\ref{fig:Causes}). Since the scarcity of water resources is directly perceptible and sensitive for utilization, its stresses on societies is one of the most striking drivers to regime shifts within human-water systems \cite{qinFlexibilityIntensityGlobal2019}.
% 水资源倾向性
(2) Secondly, the non-provisioning part of water demands growths with secondary and tertiary industries developing, leading priority of water utilization continually tilted to the socio-economic part. As original region of Ancient Chinese Civilization, the Yellow River Basin used to be dominated by agricultural but in its way to an energy industry zone now \cite{WillEnergyBases}. As a result, saving water consumption in agriculture and making concessions for industry and energy is widely recognized as solutions for the competing \cite{xiangWillEnergyIndustry2016,bebbWaterRightsTransfers2011}. Anyhow, this changes of priority reflect a truth that growing socio-economic parts are throwing feedbacks to scarcity of water resources and contributing to regime shifts.
% 水资源格局
(3) Thirdly, with closer socio-economic ties and stiffer competition between regions and sectors, the geographic scope of water resource supply and demand allocation is expanding, leading to changing configurations of water utilization. In the Yellow River Basin, the gap in water consumptions between regions and sectors are narrowing, as the result of a carefully designed allocation \cite{wangThirtyYearsYellow2018}. However, the allocation of water utilization is determined on the basis of regional and sectoral economic contexts and development trajectories\cite{wangThirtyYearsYellow2018}. The changes in water utilization configurations along with regime shifts, therefore, are the outcomes of feedback loops within complex human-water systems.

@@

	\subsection*{Integrated Water Resources Utilization (IWRU) Index}
	The Integrated Water Resources Utilization (IWRU) Index consists of three dimensions (stresses, priority and configurations, denoted by sub-indicators correspondingly). Assuming they have equal weights, we log-transformed and standardized the three sub-indicators for elimination of differences between indicators. It means for each indicator $I_{sub}$, we performed:
	$$ I' = log(I_{sub}) $$
	$$ I = (I' - I'_{min}) / (I'_{max}-I'_{min})$$
	where $I$ is standardized series for $I_{sub}$.
	Then, since we assumed different relationships between development and sub-indicators, we added them together in equal weights:
	$$ IWRU = \sum_{i}^3 I'_i $$
	where $i$ is stress, priority or configuration, and $I'_i$ is standardized sub-indicator of them. A brief description of the sub-indicators used to measure each dimension follows (see SI Methods. S3 for more details).

@@

	\subsubsection*{Sub-indicator of configurations}
	To description of configurations between regions or sections, we designed an indicator by imitation of information entropy (Allocational Entropy Metric, see supplementary document: Methods S4). Assuming the most egalitarian water allocation is assumed to be that each region or sectoral development utilizes the same proportion of water resources (the case of maximum entropy). The ratio between the actual water allocation entropy and this maximum entropy is the allocation entropy index.
	$$ ratio = \frac{Entropy}{Entropy_{max}} $$
	where $Entropy$ and $Entropy_{max}$ are entropy and maximum entropy of water distributions, respectively. They can be calculated by:
	$$ Entropy = \sum_{i=1}^n \sum_{j=1}^m -log(p_{ij}) * p_{ij} $$
	$$ Entropy_{max} = n * \sum_{j=1}^m -\frac{p_j}{n} * log(\frac{p_j}{n}) $$ 
	where $p_j$ and $p_ij$ are proportions of water use in sector $j$ and region $i$:
	$$ p_j = \frac{\sum_{i=1}^n WU_j}{\sum_{i=1}^n WU} $$
	$$ p_{ij} = \frac{WU_{ij}} {\sum_{i=1}^n \sum_{j=1}^m WU_{ij}} $$
	where $n$ is the total number of regions ($n=4$ here, see supplementary Methods. S1) and $m$ is the total number of sectors ($m=4$ here, see supplementary Methods. S2).
